Response to the defense feedback

### 2021-05-31 changelog.tex
Updates from Overleaf

\maketitle
Thank you for reviewing my dissertation. I have gone through the details of each comment and revised my dissertation multiple rounds to eliminate any logic flows and fix all the typos and grammar errors. In summary, the revisions cover the following aspects.

@@

I have a few choices to address the limitation. First, I can use static methods (verification or static program analysis). Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research. There are many papers on static side-channel analysis. Nearly all of these tools are used to prove the absence of side-channel leakages. However, most of them have high false-positive rates.

@@

The situation is a little different for a machine learning library. In my dissertation, we also evaluated Quincunx on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get correct results. The good news is that the most well-known data in machine learning is i.i.d. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. We believe the dataset is i.i.d..

@@

Dr. Larus helped me fix many grammar issues. I also revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.

>>>>

\maketitle
Thank you for reviewing my dissertation. I have gone through the details of each comment and revised my dissertation multiple rounds to eliminate any logic flows and fix all the typos and grammar errors. In summary, the revision covers the following aspects.

@@

I have a few choices to address the limitation. First, I can use static methods (verification or program analysis). Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research. There are many papers on static side-channel analysis. Nearly all of these tools are used to prove the absence of side-channel leakages. However, most of them have high false-positive rates.

@@

The situation is a little different for a machine learning library. In my dissertation, we also evaluated Quincunx on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get correct results. The good news is that the most well-known data in machine learning is i.i.d. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. We believe the i.i.d. assumption holds under the circumstance.

@@

Dr. Larus helped me a lot on fixing grammar issues. I also revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
